---
title: "ST301_A1_S17_314"
author: "S/17/314"
date: "2022-11-06"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

An insurance company wants to develop a model to predict the annual medical claims made
by its customers. The data analytic team of the company assumes that the following variables may be useful in predicting the annual medical claims made by a given policyholder. 

1. age : age of the policyholder
2. gender : the policyholder’s gender - female, male
3. bmi : body mass index of the policyholder
4. num dependents : number of dependents covered by the health insurance (spouse and children below age 18)
5. is smoker : smoking status of the policyholder - yes, no
6. working env : working environment of the policyholder - construction site, factory, office
7. tot claims : total amount of claims made by the policyholder


Read data from insurance claims.csv
 
### read the data set
```{r}
insurance_claims <- read.csv("data/insurance_claims.csv")
head(insurance_claims)
```


```{r}
attach(insurance_claims)

```

### view the data set

```{r}
View(insurance_claims)
```


# Exploratory Data Analysis

This data set contains 3 categorical variables. Before fitting the model, we should  convert categorical variables to numerical variables.

```{r}
insurance_claims$sex <- as.numeric(factor(insurance_claims$sex,labels= c("male","female")))
insurance_claims$working_env <- as.numeric(factor(insurance_claims$working_env,labels = c("construction site","factory","office")))
insurance_claims$is_smoker <- as.numeric(factor(insurance_claims$is_smoker, labels = c("yes","no")))
head(insurance_claims)
```

### the number of column
```{r}
dim(insurance_claims)
```
### to display containt of the list
```{r}
str((insurance_claims))
```
```{r}
pairs(~age+sex+bmi+children+is_smoker+working_env+tot_claims, data = insurance_claims)

```

# Model Fitting

we use forward selection method and adjusted R-squard as variable selection method.


## Iteration 01

```{r}
summary(lm(tot_claims~age,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(formula = tot_claims~sex,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(formula = tot_claims~bmi,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(formula = tot_claims~children,data = insurance_claims))$adj.r.squared
```

```{r}
summary(lm(formula = tot_claims~is_smoker,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(formula = tot_claims~working_env,data = insurance_claims))$adj.r.squared
```
 Working_env is added to the model.



## Iteration 02

```{r}
summary(lm(formula = tot_claims~working_env+age,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(formula = tot_claims~working_env+sex,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+bmi,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+children,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+is_smoker,data = insurance_claims))$adj.r.squared
```
Age is added to the model.



## Iteration 03

```{r}
summary(lm(tot_claims~working_env+age+sex,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+age+bmi,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+age+children,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+age+is_smoker,data = insurance_claims))$adj.r.squared
```
is_smoker is added to the model.

## Iteration 04

```{r}
summary(lm(tot_claims~working_env+age+is_smoker+sex,data = insurance_claims))$adj.r.squared
```

```{r}
summary(lm(tot_claims~working_env+age+is_smoker+bmi,data = insurance_claims))$adj.r.squared
```
```{r}
summary(lm(tot_claims~working_env+age+is_smoker+children,data = insurance_claims))$adj.r.squared
```
bmi is added to the model.



## Iteration 05

```{r}
summary(lm(tot_claims~working_env+age+is_smoker+bmi+sex,data = insurance_claims))$adj.r.squared
```

```{r}
summary(lm(tot_claims~working_env+age+is_smoker+bmi+children,data = insurance_claims))$adj.r.squared
```
## children is added to the model.



#Iteration 06

```{r}
summary(lm(tot_claims~working_env+age+is_smoker+bmi+children +sex,data = insurance_claims))$adj.r.squared
```
sex is added to the model.


# Graph of Adjusted R-squared values

```{r}
plot(c(0.8614734,0.886051,0.9013036,0.9063182,0.9085069,0.9085106),xlab = "Number of variables in the model",ylab ="Adjusted R-squared", type="o")
```

# Backward selection based on F-Test

```{r}
full.model <- lm(tot_claims ~ ., data = insurance_claims)
drop1(full.model, test = "F")

```

Variable sex has the highest p value(>0.05). It is not significant then we can Drop sex variable from the model.

```{r}
drop1(full.model, .~. -sex,test = "F")
```
all the variables have p values less than 0.05. All variables are significant.


# Reduced Model

```{r}
red_model <- lm(tot_claims ~ working_env+ age + bmi + children + is_smoker, data = insurance_claims)
summary(red_model)

```
All the variables have p values less than 0.05 and since adj R-squared value is 0.9085 this model is significant.


# Validation

In Here we use partial F test for Hypothesis testing

Null Hypothesis : Reduced model is adequate vs
Alternative Hypothesis : Reduced model is not adequate

```{r}
anova(red_model,full.model)
```

According to the anova table, p value of fitted line is greater than 0.05. so we do not have enough evidence to reject null hypothesis.
We can say that the reduced model is adequate.


# Residuals

```{r}
par(mfrow = c(2,2))
plot(red_model)
```

This reduced model has some outliers. First, we have to remove the outliers.

```{r}
Q1 <- quantile(insurance_claims$tot_claims, .25)
Q3 <- quantile(insurance_claims$tot_claims, .75)
IQR <- IQR(insurance_claims$tot_claims)
insurance01 <- subset(insurance_claims,insurance_claims$tot_claims > (Q1 -1.5*IQR) & insurance_claims$tot_claims < (Q3+1.5*IQR))
dim(insurance01)

```
```{r}
attach(insurance01)
```



```{r}
reduced_model01 <-lm(tot_claims~working_env+age+is_smoker+bmi+children,data = insurance01)
```
```{r}
hist(insurance01$tot_claims)

```
```{r}
red_model <- lm(tot_claims ~ working_env+ age + bmi + children + is_smoker, data = insurance01)
par(mfrow = c(2, 2))
plot(red_model)
```


# conclustion

After removing the outliers, assumptions are not violated.

```{r}
coef(red_model)
```
Fitted Model is ,
tot_claims=23367.01967-(9731.74438)working_env + (165.14881)age + (16.46953)bmi + (463.30489)children + (5029.076)is_smoker
